Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-05 talk/dls2014/paper/paper.tex
tweaks

Our contributions include:
\begin{itemize}[noitemsep]
\item We introduce a new software transactional memory (STM) system
  that performs well on low numbers of CPUs.
\item We make novel use of the memory management capabilities of
  off-the-shelf CPUs, e.g. memory segmentation and 64bit address space.
\item We integrate our STM system closely with a garbage collector
  (GC) in order to lower the overhead of STM.
\item This new STM system is used to replace the GIL in one
  implementation of Python and is then evaluated extensively.
\item We introduce atomic blocks to the Python language to provide a
  backwards compatible, composable synchronisation mechanism for
  threads.
\end{itemize}

@@

What we described so far has no mesurable performance impact by itself,
but is missing conflict detection to be part of a full-fledged STM
system.  This requires adding \emph{barriers} to the program to register
the objects into the read or write set, and adapting the commit
protocol in consequence.

@@

% \bibitem{felber07}
%   Felber, Pascal, et al. "Transactifying applications using an open
%   compiler framework." \emph{TRANSACT}, August (2007): 4-6.

>>>>

Our contributions include:
\begin{itemize}[noitemsep]
\item We introduce a new software transactional memory (STM) system
  that performs well on low numbers of CPUs.
\item We make novel use of the memory management capabilities of
  off-the-shelf CPUs, e.g. memory segmentation and 64bit address space.
\item We integrate our STM system closely with a garbage collector
  (GC) in order to lower the overhead of STM.
\item This new STM system is used to replace the GIL in one
  implementation of Python and is then evaluated.
\item We introduce atomic blocks to the Python language to provide a
  backwards compatible, composable synchronisation mechanism for
  threads.
\end{itemize}

@@

What we described so far has no mesurable performance impact by
itself, and it is missing conflict detection to be considered a
full-fledged STM system.  This requires adding \emph{barriers} to the
program to register the objects into the read or write set before
reading or writing to them\footnote{Barriers added by an automatic and
local program transformation~\cite{felber07}}.  Furthermore, we need
to describe the commit protocol.

@@

\bibitem{felber07}
  Felber, Pascal, et al. "Transactifying applications using an open
  compiler framework." \emph{TRANSACT}, August (2007): 4-6.
